
\begin{flushleft}
The internship at DreamOnline Limited was my first experience working in a software company.It gave me everything an engineering graduate student could ask for. I collaborated extensively with management, field engineers, scrum team members, and software developers. This gave me the opportunity to develop not only my teamwork abilities but also my interpersonal and collaborative skills.

\vspace{20pt}

Amongst other tasks, I was totally responsible for the development of the software throughout
the cycle. As a result, I was highly particular and detail-oriented about everything. By doing this internship I get to know how a product is built, the allocation of work as well as the time and budget concerns of a project. Before my internship, I always believed that software engineering is all about coding, but now this belief of mine is broken. There is a lot of thinking going on before building software and solving a problem in software engineering.

\vspace{20pt} 

From a technical point of view, I worked with various tools and technologies in this internship.
This internship was incredibly beneficial for me because it has given me the opportunity to learn
about new working cultures and advance my technical skills. I solved a lot of real-life business
problems during my internship. Definitely, the road wasn’t easy. I faced plenty of challenges and
limitations but I was able to overcome all the hurdles.

\vspace{20pt}

As an intern, it was a great experience working at DreamOnline Limited. I am grateful to the
Department of Computer Science and Engineering of Islamic University Technology (IUT) for
this experience. Because of this experience, I am able to link my academic and professional
development and gain an understanding of the significance of the university courses we all took.
I also came to understand my weaknesses and the areas I'll be focusing on to improve as a
person and a software developer.

\vspace{20pt}


I am satisfied with the work accomplished and the impact made at DreamOnline Limited. I'm
confident that this internship is a crucial milestone in the development of my career in the
profession.
\end{flushleft}