\setcounter{section}{0} 

One of the leading providers of IT outsourcing services is DreamOnline Limited.They have clients from
all over the world. The company also has some in-house products which serve a huge number
of users. They follow agile methodologies while developing the products. A team of highly
skilled engineers who have expertise in their respective fields continuously works to meet the
client's requirements and deliver an impressive product.
\section{Services provided by the Company}
\begin{flushleft}
The company's offshore software development services are geared to deliver results that are
expected from a Japanese IT outsourcing company. DreamOnline Limited offers clients a final
product that will aid in the expansion of their company in addition to software development and
maintenance services. The services that the company provides are

\begin{itemize}
    \item \textbf{Mobile Application Development}\\
    \vspace{6pt}
DreamOnline has extensive experience in creating mobile apps and has developed over
800 apps to date. They have developed apps across multiple industries and
technologies, including AR/VR/AI/ML.
\item \textbf{Web Application Development}\\
\vspace{6pt}
Dedicated web application development team of experts brings in over 10 years of
domain experience. They have developed a wide range of products for various
industries. They have already established their name as a leading software company for
developing great web services.
\item \textbf{Windows/Linux/Mac Application Development}\\
\vspace{6pt}
DreamOnline has developed a variety of platforms using Win / Mac / Linux based on
different clients' business needs and providing innovative solutions to their problems.
\item \textbf{AR/VR Applications}\\
\vspace{6pt}
The company already developed a good number of applications using AR/VR
technologies. They support a wide range of systems from on-site systems to game
systems used at events.
\item \textbf{IoT Applications}\\
\vspace{6pt}
DreamOnline developed desktop apps and smartphone apps that work with hardware
devices. They have some impressive IoT applications that solve a lot of common
problems.
\item \textbf{ML/AI Applications}\\
\vspace{6pt}
The company also has expertise in developing ML/AR applications. The company mainly
develops its apps using Apple's Core ML and Google's ML Kit.
\end{itemize}


Multiple products using different tools and technologies are developing simultaneously. The
company follows both teams oriented as well as project-oriented approaches while developing
its products depending on the requirements.

\end{flushleft}





