\setcounter{section}{0} 
The company believes in the fundamental idea that creative work requires a special kind of work
culture. The company takes great initiative to create a work culture that attracts talented people
and supports them in giving their best work. This culture is evident in everything from workplace
structure to the development teams' guiding principles.

\section{Company Working Environment \& Protocols}
\begin{flushleft}
Having a great culture in the workplace increases a person’s productivity and helps him/her to
achieve personal and professional goals.
Some noteworthy workplace cultures I encountered in DreamOnline Limited are 
\begin{itemize}
    \item \textbf{Helpful \& Considerate}\\
    \vspace{6pt}
The company has an environment where employees can easily get help from their
colleagues. Coworkers push each other to bring out the best in each. If you get stuck in
some problems there will be someone who is ready to help you. Having such a positive
workplace culture improves teamwork, raises morale, increases productivity and
efficiency, and enhances retention of the workforce.
At the same time, the company is very considerate of an employee's time and effort.
They never push an employee to work overtime or extra hour. Being in a healthy mindset
is the most important thing for being productive in the workplace.
    \item \textbf{ Comfortable Workplace}\\
    \vspace{6pt}
Comfortable workspaces with amenities and perks that people care about contribute
significantly to morale levels. People have the flexibility to join the office from home or
join the office physically. The on-site office has all the facilities that an employee needs
to do his/her day-to-day tasks. Even in the online office, everything is very organized.
We can communicate with anyone without any problems. Gossip or office politics have
no place in a productive workplace. Even if this occasionally occurs in group settings, it
ought to be the exception rather than the rule.
\item \textbf{ Effective communication}
\vspace{6pt}
Communication is the most important thing when it comes to working in a team. A
culture of fear and uncertainty is cultivated by secrecy or a lack of communication from
the top to down. By having effective communication we can avoid information overload
and cut down on unnecessary things that are not relevant to work. DreamOnline Limited
put a strong emphasis on creating an effective communicative environment in the
workplace. Coworkers can easily communicate with each other whether they are working
in a physical office or in a home office. In the company, regular audits are conducted to
assess how individuals are interacting with one another, input is accepted and
considered, and possibilities for social connection are made possible by open and
honest communication.
\item \textbf{Supportive Environment}
\vspace{6pt}
The most important thing I like about working in this company is they really appreciate
your hard work, efforts, and time. In my opinion, a good work environment is one where
all employees—regardless of their gender, sexual orientation, or skin color—are valued,
encouraged, and fostered. All employees ought to enjoy equal access to all benefits and
rewards offered, as well as equal opportunities to advance.
\item \textbf{ Enjoyable Work Culture}
\vspace{6pt}
As an appreciation for the employee's hard work, the company regularly arranges events
and parties for them. All wins like launching a mobile app or releasing a product are
celebrated. These types of things motivate employees to work even harder and deliver
amazing results. By doing these, employees get to know each other more and as a
result, it creates a healthy and friendly environment in the workplace
\item \textbf{Constructive Feedback}\\
\vspace{6pt}
The success of a team depends on feedback. DreamOnline Limited does not hide the
truth when providing feedback out of concern for a disagreement. Regularly giving
honest comments will help the team improve. The best strategy is to start frequent
feedback sessions. All team members can provide genuine feedback on the
performance of the team during these meetings.
\end{itemize}

\end{flushleft}

\section{Events}
\begin{flushleft}
\begin{itemize}
    \item \textbf{Meetings}\\
    \vspace{6pt}
Every morning I had to join the morning scrum meeting where I have to tell the team
what I did the previous day and what I am going to do today. Usually, we have our team
meeting 3 to 4 times every week where we discussed the progress of the project as well
as the things we need to do to meet the deadlines.
I also had to join a security meeting that generally happened in the 1st week of every
month where my senior manager briefed all the employees about the security policies
and rules and regulations of the company.
\item \textbf{Parties}\\
\vspace{6pt}
During my stay in the company, there were three dinner parties, one lunch party, and
one summer fruit festival. I joined most of them. By attending the party, I get to know a
lot of amazing and talented people. It was such a great experience for me. People from
different teams share their experiences of working with different tools and technologies
and that really motivates me to learn even more.
\item \textbf{Tours}\\
\vspace{6pt}
Sometimes a team or sometimes the whole office goes on a trip together so that they
can get rid of stressful work and enjoy life. This helps in team bonding as well as makes
people more motivated to do their work.
\end{itemize}
   


\end{flushleft}

\section{Performance Rewards}
\begin{flushleft}
    The company values the people who have a great impact on the company. As an appreciation
for their hard work, the company rewards those employees and promotes them. Every year
some employees get the Employee of the Year award for their amazing work. This type of
culture not only motivates those employees who got rewards but also others to push their limits
and become more skilled. Even when a person works overtime or on weekends, they get extra
benefits from the company.

\end{flushleft}


\section{Internee Policy}
\begin{flushleft}
    As an intern, I was also treated as a regular employee. They always valued my opinions and
gave feedback about my work. I had to attend all the official meetings. Generally, the company
assigns a mentor to the intern and gives them enough time to learn about the codebase and
necessary technologies.\\
\vspace{6pt}
Usually, when an intern joined the company, they give priority to what technologies the intern
want’s to work with. The company’s policy about interns is they don’t hire fresh graduates
directly. They first offer internships to potential candidates and if they perform well during the
internship, they get the offer to join the company as full-time employees.\\
\vspace{6pt}
The company follows a guideline for new interns. The interns have to follow this guideline and
abide by the rules and regulations of the company.

\begin{itemize}
    \item All interns will be assigned to a team first\\
 \item Interns going to report to his/her immediate supervisor\\
 \item The company allocated a learning phase for new interns before assigning them new
tasks. They can take help from their respective team members.\\
 \item The company can assign the intern to a different team if required. Interns also get the
choice to choose their preferable technologies.\\
 \item Interns will get a full-time employment offer if they do well during the internship
\end{itemize}

\end{flushleft}